---
title: "Simple document"
output:   
  html_document: 
    toc: true
    toc_float: true
    code_folding: hide
---

```{r, message = FALSE}
library(tidyverse) # Best practice to load all libraries at beginning of .Rmd
```

I'm an R Markdown document! 

For HTML: 
```{r, eval=FALSE}
output:   
  html_document: 
    toc: true
    toc_float: true
    code_folding: hide
```

For PDF: 
```{r, eval=FALSE}
output: pdf_document
```

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.
To round the output, we can use `round(mean(samp), 2)`.

# Section 3

This is going to make a plot! 
Use option + Cmd + I to make a new chunk. 

First I generate a dataframe, then use `ggplot` to make a scatterplot.

```{r chunk_scatterplot}
plot_df = 
  tibble(
    x = rnorm(n = 1000), #Standard normal distribution
    y = 1 + 2 * x^2 + rnorm(n = 1000)
  )

ggplot(plot_df, aes(x = x, y = y)) + geom_point()

```
```{r chunk_histogram, echo = FALSE}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

## Learning assessment

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. 

Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. 

What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

```{r}
df = tibble(
  var_numeric = rnorm(500, mean = 1),
  var_logic = var_numeric > 0, 
  var_abs = abs(var_numeric)
)

ggplot(df, aes(x = var_abs)) + geom_histogram()
```

The median of the variable containing absolute values is 
`r round(median(df$var_abs), 2)`.

